\section{Expected Results}
\label{sec:expected_results}

In this project, the experiments will be run on the
in-house HPC system, \textit{Innovation}, at the Computer Architecture
and Systems Research Laboratory (CASTL). Multiple types of basic
shortest path algorithms will be implemented, and the runtime
performance and outcomes will be recorded.
Later, different clustering techniques will be applied to segregate
the dataset into subsets and algorithms described in Sec.~\ref{sec:methodology}
will be implemented. The parallel application will be run on \textit{Innovation}
such that each unit or component in the system deals with the data in each cluster.
Finally, all the separate results of each component will be aggregated and the total
runtime performance will be recorded. The final result for a specific
shortest path algorithm will be compared to the outcomes that were found
using the basic algorithm. Thus, the accuracy of the clustering technique will
be reported.

Hence, the research is expected to deliver the following results:
\begin{itemize}
    \item Application for clustering dataset, application to implement basic shortest path algorithms, parallel application to implement algorithm on clustered data.
    \item Runtime performance and outcomes from different basic shortest path algorith without clustering.
    \item Runtime performance and outcomes from different shortest path algorith with clustering.
    \item Intuitive comparison among differnt clustering techniques and the associated results.
    \item Evaluation of the accuracy of each clustering technique compared to the ideal results by the basic algorithms.
\end{itemize}
